An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-16 neurips-19/poly-embed.tex
small top-k edits
Updated figures
Minor typos

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}
\newcommand{\elltopk}{\ell_{\text{top-$k$}}}

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.

@@

%transition here
\begin{figure}
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/original-top-k}
	\caption{The minimizers of the $top-2$ loss $\ell_{top-2}$ as a function of $p$.}
	\label{fig:original-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
	\caption{Level sets for the minimizers of $\inprod{p}{L(\cdot)}$.}
	\label{fig:convex-surrogate-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
	\caption{The finite property $\prop{L|_\R}$}
	\label{fig:finite-surrogate-top-k}
\end{minipage}
\end{figure}

@@

\section{Top-$k$ surrogate}
Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.

>>>>

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}
\newcommand{\elltopk}{\ell_{\text{top-$k$}}}
\newcommand{\elltop}[1]{\ell_{\text{top-$#1$}}}

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.

@@

%transition here
\begin{figure}
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/original-top-k}
	\caption{Minimizers of $\elltop{2}$ as a function of $p$.}
	\label{fig:original-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/convex-surrogate-top-k}
	\caption{Minimizers of $L_2$ as a function of $p$.}
	\label{fig:convex-surrogate-top-k}
\end{minipage}
\hfill
\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
	\caption{Minimizers of $\ell$ as a function of $p$.}
	\label{fig:finite-surrogate-top-k}
\end{minipage}
\end{figure}

@@

\section{Top-$k$ surrogate}
\jessie{Can scrap Lemma 13... not sure the point of Lemma 12 on its own, but it might be worth keeping.  Thoughts?}
Throughout this section, consider the surrogate and discrete loss $L'(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell'(r)_y = \Ind{y \not\in r} + \frac{1}{k} |r \setminus \{y\}|$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.
